\vspace{-1em}Guidance, please! Towards a framework for RDF-based constraint languages.

### 2015-07-08 paper/paper 2/dc-2015.tex
related work

\emph{Stardog ICV} and \emph{Pellet ICV} use OWL 2 constructs to formulate constraints. The \emph{Pellet Integrity Constraint Validator (ICV)} is a proof-of-concept extension for the \emph{OWL 2 DL} reasoner \emph{Pellet}. \emph{Stardog ICV} validates RDF data stored in a Stardog database according to constraints which may be written in SPARQL, OWL, or SWRL.

\emph{ShEx} specifies a language whose syntax and semantics are similar to regular expressions.
\emph{ShEx} associate RDF graphs with labeled patterns called \emph{shapes} 
which are used to express formal constraints on the content of RDF graphs.

\emph{ReSh} defines its own vocabulary for specifying \emph{shapes} of RDF resources.
Ryman et al. define \emph{shape} as a description of the set of triples a resource is expected to contain and of the integrity constraints those triples are required to satisfy \cite{Ryman2013}.

\emph{DCMI RDF Application Profiles (AP)} and \emph{Bibframe} are approaches to specify profiles for application-specific purposes. 
\emph{DCMI RDF-AP} uses \emph{DSP} as generic constraint language which is also intuitive for non-experts.
The \emph{Bibliographic Framework Initiative (Bibframe)} defines a vocabulary which has a strong overlap with \emph{DSP}.

Kontokostas et al. define 17 data quality integrity constraints represented as \emph{SPARQL} query templates called \emph{Data Quality Test Patterns (DQTP)} \cite{Kontokostas2014}.

@@

>>>>

\emph{Stardog Integrity Constraint Validation (ICV)} and the \emph{Pellet Integrity Constraint Validator (ICV)} use OWL 2 constructs to formulate constraints. The Pellet ICV is a proof-of-concept extension for the OWL 2 DL reasoner \emph{Pellet} \cite{sirin2007pellet}. Stardog ICV validates RDF data stored in a Stardog database according to constraints which may be written in SPARQL, OWL 2, or SWRL \cite{Horrocks04}.

\emph{Shape Expressions (ShEx)} \cite{W3C-ShEx-Primer-2014,W3C-ShEx-Definition-2014,Prud'hommeaux-2014,Boneva-2014} specifies a language whose syntax and semantics are similar to regular expressions. ShEx associate RDF graphs with labeled patterns called \emph{shapes} which are used to express formal constraints on the content of RDF graphs. \emph{Resource Shapes (ReSh)} \cite{W3C-ReSh-2014} defines its own vocabulary for specifying shapes of RDF resources. Ryman, Hors, and Speicher define \emph{shape} as a description of the set of triples a resource is expected to contain and as a description of the integrity constraints those triples are required to satisfy \cite{Ryman2013}.

\emph{DCMI RDF Application Profiles (AP)} and \emph{Bibframe} are approaches to specify profiles for application-specific purposes. 
\emph{DCMI RDF-AP} uses \emph{DSP} as generic constraint language which is also intuitive for non-experts.
The \emph{Bibliographic Framework Initiative (Bibframe)} defines a vocabulary which has a strong overlap with \emph{DSP}.
Kontokostas et al. define 17 data quality integrity constraints represented as \emph{SPARQL} query templates called \emph{Data Quality Test Patterns (DQTP)} \cite{Kontokostas2014}.

@@

\tb{SHACL}
